Outdated and License-Violating Code on Stack Overflow

### 2017-08-15 cloverflow-tse/cloverflow.tex
Latest update to the paper.

\textbf{Clone Detection Tools: } We use clone detection to discover online code
clones. %\textbf{Clone Detection and Configuration: }
There are a number of restrictions in terms of choosing the clone detection
tools for this study. The main restriction is due to nature of code snippets
posted on Stack Overflow, as most of them are incomplete Java classes or
methods. Hence, a detector must be flexible enough to process code snippets that
are not compilable or not complete blocks. Moreover, since the amount of code
that has to be processed is in a scale of millions line of code (as shown in
\Cref{tab:datasets}), a clone detector must be scalable enough to report clones
in a reasonable amount of time. We have tried 7 state-of-the-art clone detectors
including Simian~\cite{simian}, SourcererCC~\cite{Sajnani2016},
NiCad~\cite{Cordy,Roy2008}, CCFinder~\cite{Kamiya2002}, iClones~\cite{Gode2009},
DECKARD~\cite{Jiang2007a}, and PMD-CPD~\cite{pmd-cpd} against the Stack Overflow
and Qualitas datasets. NiCad failed to parse 44,960 Stack Overflow snippets
while PMD CPD failed to complete the execution. Although Simian, SourcererCC,
CCFinder, iClones, and DECKARD could successfully report clones, we decided to
choose Simian and SourcererCC due to their fast detection speed.

\textbf{Simian} is a text-based clone detector that locates clones at line-level
granularity and has been used extensively in several clone
studies~\cite{Ragkhitwetsagul2016, Wang2013, Mondal2011, Cheung2015,
	Krinke2010}. Furthermore, it offers normalisation of variable names and literals
(strings and numbers) which enables Simian to detect literal clones (type-1) and
parameterised clones (type-2). \textbf{SourcererCC} is a token-based clone
detector which detects clones at either function- or block-level granularity. It
can detect clones of type-1, -2 up to type-3 (clones with added and removed
statements) and offer scalability against large code
corpus~\cite{Sajnani2016,Saini2016,Yang2017}. Due to incomplete code blocks and
functions normally found in Stack Overflow snippets, the built-in Java tokeniser
could not parse more than half of all snippets. SourcererCC provides an option
to plug in a customised tokeniser, so we developed a special Java tokeniser with
assistance from the tool's creator. Another benefit of SourcererCC is its
indexing and search processing allows us to detect code clones between two
systems.

We prepared the Java code in both datasets by removing comments and
pretty-printing to increase the clone detection accuracy. Then, we deployed the
two detectors to locate clones between the two datasets.  For each Qualitas
project, we ran the tools on the project's code and the entire Stack Overflow
data. Simian did not provide an option to detect cross-project clones. Hence the
Simian clone report was filtered to contain only clone pairs between Stack
Overflow and Qualitas projects, removing all clone pairs within either Stack
Overflow or within Qualitas.

\begin{table}
	\centering
	\caption{Configurations of Simian and SourcererCC}
	\label{t:param_tuning}
%		\resizebox{\columnwidth}{!}{
	\small
	\begin{tabular}{lp{5cm}}
		\toprule
		Tool & Configurations \\
		\midrule
		Simian~(\textit{S}) &  Threshold=10, ignoreStringCase, \newline ignoreCharacterCase, \newline ignoreModifiers \\ 
		\midrule
		SourcererCC~(\textit{SCC}) & Functions, Minimum clone size=10, \newline Similarity=80\% \\
		\bottomrule
	\end{tabular} %
%	}
\end{table}

\textbf{Clone Detection Configuration: }
We are aware of effects of configurations to clone detection results
and the importance of searching for optimised configurations in
empirical clone
studies~\cite{Svajlenko2014,Wang2014,cr2016ssbse,Ragkhitwetsagul2016}. However,
considering the massive size of the two datasets and the search space
of at least 15 Simian and 5 NiCad parameters, we are unable to search
for the best configurations of the tools. Thus, we decided to
configure Simian and NiCad using two established configurations:
(1)~the tools' default configurations chosen by the tools' creators
(denoted as \textit{D}), and (2)~the discovered configurations for
Bellon's Java projects from \textit{EvaClone}~\cite{Wang2013}, a study
of optimising clone detectors' configurations based on clone agreement
(denoted by \textit{E}). \Cref{t:param_tuning} shows the two configurations.
In total, we have four configurations: Simian with the default
configuration ($S_D$), Simian with the EvaClone configuration ($S_E$), 
NiCad with the default configuration ($N_D$)
and NiCad with the EvaClone configuration ($N_E$).

We encountered NiCad failures with a few Qualitas projects.~$N_D$
could not detect clones in \textsf{hibernate} due to clustering
errors. $N_E$ generated errors during code normalisation for 5
projects including \textsf{vuze}, \textsf{hibernate},
\textsf{myfaces}, \textsf{netbeans}, and \textsf{spring}. We have
contacted the creator of NiCad regarding the issues. They identified
the issues as problems in the TXL grammar and as problems of long file
paths, and will be fixed in the next NiCad releases.

The number of online clone pairs reported % by running Simian and NiCad
are presented in \Cref{tab:orig_stats}. $S_D$ reports 67,570 clone
pairs while $N_D$ reports 632,855 clone pairs. $S_E$ and $N_E$ report
much larger numbers of clone pairs, 63,635,844 and 251,449,849 pairs
respectively. This is expected since EvaClone configurations prefer
recall~\cite{Wang2013}.  The average clone size reported by $S_D$ is
9.11 lines which is bigger than for $S_E$ (5.95 lines). Similarly,
$N_D$ has an average clone size of 10.85 lines which is bigger than
6.28 lines reported by $N_E$. The drop in size is due to the EvaClone
configuration with a smaller minimum size (\Cref{t:param_tuning}).

\begin{table}
	\centering
	\caption{Number of online clones reported by Simian and SourcererCC}
	\label{tab:orig_stats}
	%\small
	%\resizebox{\columnwidth}{!}{%
	\begin{tabular}{lrr}
		\toprule
		Stats & \multicolumn{1}{c}{Simian} & \multicolumn{1}{c}{SourcererCC} \\
		\midrule
		Total clone pairs & 721 & 1,678 \\
		Average clone size & 16.61 & 17.86 \\
		\bottomrule
	\end{tabular} %
	%}
\end{table}

>>>>

\textbf{Clone Detection Tools: } We use clone detection to discover online code
clones. %\textbf{Clone Detection and Configuration: }
There are a number of restrictions in terms of choosing the clone detection
tools for this study. The main restriction is due to nature of code snippets
posted on Stack Overflow, as most of them are incomplete Java classes or
methods. Hence, a detector must be flexible enough to process code snippets that
are not compilable or not complete blocks. Moreover, since the amount of code
that has to be processed is in a scale of millions line of code (as shown in
\Cref{tab:datasets}), a clone detector must be scalable enough to report clones
in a reasonable amount of time. We have tried 7 state-of-the-art clone detectors
including Simian~\cite{simian}, SourcererCC~\cite{Sajnani2016},
NiCad~\cite{Cordy,Roy2008}, CCFinder~\cite{Kamiya2002}, iClones~\cite{Gode2009},
DECKARD~\cite{Jiang2007a}, and PMD-CPD~\cite{pmd-cpd} against the Stack Overflow
and Qualitas datasets. NiCad failed to parse 44,960 Stack Overflow snippets
while PMD CPD failed to complete the execution due to lexical errors. iClones
could complete its execution but skipped 367 snippets due to malformed blocks in
Stack Overflow data set. Although Simian, SourcererCC, CCFinder, and DECKARD
could successfully report clones, we decided to choose only Simian and
SourcererCC due to their fast detection speed.

\textbf{Simian} is a text-based clone detector that locates clones at line-level
granularity and has been used extensively in several clone
studies~\cite{Ragkhitwetsagul2016, Wang2013, Mondal2011, Cheung2015,
	Krinke2010}. Furthermore, it offers normalisation of variable names and literals
(strings and numbers) which enables Simian to detect literal clones (type-1) and
parameterised clones (type-2). \textbf{SourcererCC} is a token-based clone
detector which detects clones at either function- or block-level granularity. It
can detect clones of type-1, -2 up to type-3 (clones with added and removed
statements) and offer scalability against large code
corpus~\cite{Sajnani2016,Saini2016,Yang2017}. Another benefit of SourcererCC is
its indexing and search processing allows us to detect code clones between two
systems.

We prepared the Java code in both datasets by removing comments and
pretty-printing to increase the clone detection accuracy. Then, we deployed the
two detectors to locate clones between the two datasets.  For each Qualitas
project, we ran the tools on the project's code and the entire Stack Overflow
data. Due to incomplete code blocks and functions
normally found in Stack Overflow snippets, the built-in SourcererCC's Java
tokeniser could not parse 45,903 snippets, more than half of them. Nevertheless,
the tool provides an option to plug in a customised tokeniser, so we developed a
special Java tokeniser with assistance from the tool's creator. The customised
tokeniser successfully processed all Stack Overflow snippets.
Simian did not provide an option to detect cross-project clones. Hence the
Simian clone report was filtered to contain only clone pairs between Stack
Overflow and Qualitas projects, removing all clone pairs within either Stack
Overflow or within Qualitas.

\begin{table}
	\centering
	\caption{Configurations of Simian and SourcererCC}
	\label{t:param_tuning}
%		\resizebox{\columnwidth}{!}{
%	\small
	\begin{tabular}{lp{5cm}}
		\toprule
		Tool & Configurations \\
		\midrule
		Simian~(\textit{S}) &  Threshold=10, ignoreStringCase, \newline ignoreCharacterCase, \newline ignoreModifiers \\ 
		\midrule
		SourcererCC~(\textit{SCC}) & Functions, Minimum clone size=10, \newline Similarity=80\% \\
		\bottomrule
	\end{tabular} %
%	}
\end{table}

\textbf{Clone Detection Configuration: } We are aware of effects of
configurations to clone detection results and the importance of searching for
optimised configurations in empirical clone
studies~\cite{Svajlenko2014,Wang2014,cr2016ssbse,Ragkhitwetsagul2016}. However,
considering the massive size of the two datasets and the search space of at
least 15 Simian and 3 SourcererCC parameters, we are unable to search for the
best configurations of the tools. Thus, we decided to configure Simian and
SourcererCC based on their established default configurations chosen by the
tools' creators. All variable renaming are disabled to decrease a number of
false positives since we aim for finding clones that are copied from open source
projects with minimal modifications. The two clone detectors complement each
other by having Simian detecting literal copies of code snippets and SourcererCC
detecting clones with added/deleted statments. We made sure that they 
detected only non-trivial clones by increasing the minimum clone size to ten
lines.
%(denoted as \textit{D}), and (2)~the discovered configurations for
%Bellon's Java projects from \textit{EvaClone}~\cite{Wang2013}, a study
%of optimising clone detectors' configurations based on clone agreement
%(denoted by \textit{E}). \Cref{t:param_tuning} shows the two configurations.
%In total, we have four configurations: Simian with the default
%configuration ($S_D$), Simian with the EvaClone configuration ($S_E$), 
%NiCad with the default configuration ($N_D$)
%and NiCad with the EvaClone configuration ($N_E$).

%We encountered NiCad failures with a few Qualitas projects.~$N_D$
%could not detect clones in \textsf{hibernate} due to clustering
%errors. $N_E$ generated errors during code normalisation for 5
%projects including \textsf{vuze}, \textsf{hibernate},
%\textsf{myfaces}, \textsf{netbeans}, and \textsf{spring}. We have
%contacted the creator of NiCad regarding the issues. They identified
%the issues as problems in the TXL grammar and as problems of long file
%paths, and will be fixed in the next NiCad releases.

The number of online clone pairs reported % by running Simian and NiCad
are presented in \Cref{tab:orig_stats}. Simian reports 721 clone
pairs while SourcererCC reports 1,678 clone pairs. 
SourcererCC reports more clones due to its capability of detecting
type-1 to type-3 clones while Simian only detects type-1 and type-2 clones.
The average clone size reported by Simian is
16.61 lines which is slightly smaller than SourcererCC (17.86 lines).

\begin{table}
	\centering
	\caption{Number of online clones reported by Simian and SourcererCC}
	\label{tab:orig_stats}
	%\small
	%\resizebox{\columnwidth}{!}{%
	\begin{tabular}{lrr}
		\toprule
		Stats & \multicolumn{1}{c}{Total clone pairs} & \multicolumn{1}{c}{Average clone size} \\
		\midrule
		Simian & 721 & 16.61 \\
		SourcererCC & 1,678 & 17.86 \\
		\bottomrule
	\end{tabular} %
	%}
\end{table}
